---
title: "Heterogeneous Treatment Effects in a Difference-in-Differences Framework"
author: "Adél Luca Szűcs"
date: ""
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE, warning=FALSE)
```

1. Objective

This note illustrates the estimation of heterogeneous treatment effects within a fixed-effects difference-in-differences (DiD) framework using panel data from a field experiment.

The objective is to evaluate whether treatment effects vary systematically with pre-treatment characteristics.

2. Data and Setup

```{r, warning=FALSE, message=FALSE}
library(foreign)
library(fixest)
library(dplyr)
library(interflex)
library(car)

theUrl <- "https://surfdrive.surf.nl/files/index.php/s/5jmKNy3xXzzppgG/download"
waste <- read.dta(theUrl)
```

The dataset contains weekly observations for garbage collection routes, with treatment assigned at the route level. The outcome variable is residual_weight, and the treatment variable is treatment_dummy.

3. Subgroup-Specific Treatment Effects

To allow for treatment heterogeneity, we define an indicator based on the median pre-treatment share of terraced houses.



```{r}
waste <- waste %>%
  mutate(high_terracedhouses = as.numeric(
    terracedhouses > median(terracedhouses, na.rm = TRUE)
  ))

waste$low_terracedhouses <- 1 - waste$high_terracedhouses
```


We estimate a fully interacted DiD model with route and week fixed effects:



```{r}
cate_binary <- feols(
  residual_weight ~
    treatment_dummy:low_terracedhouses +
    treatment_dummy:high_terracedhouses +
    treatment_period:high_terracedhouses
  | route + week,
  data = waste,
  vcov = ~route
)

summary(cate_binary)
```
The interaction terms provide subgroup-specific conditional average treatment effects (CATEs).

To test whether these subgroup effects differ statistically:

```{r}
linearHypothesis(
  cate_binary,
  "treatment_dummy:low_terracedhouses = treatment_dummy:high_terracedhouses"
)

```
4. Continuous Interaction Specification

Next, we allow treatment effects to vary continuously with the pre-treatment share of terraced houses.
```{r}
cate_continuous <- feols(
  residual_weight ~
    treatment_dummy +
    treatment_dummy:terracedhouses +
    treatment_period:terracedhouses
  | route + week,
  data = waste,
  vcov = ~route
)

summary(cate_continuous)
```
The marginal treatment effect evaluated at the mean of the moderator is:

```{r}
b0 <- coef(cate_continuous)["treatment_dummy"]
b1 <- coef(cate_continuous)["treatment_dummy:terracedhouses"]

mean_th <- mean(waste$terracedhouses, na.rm = TRUE)
cate_at_mean <- b0 + b1 * mean_th

cate_at_mean
```
5. Marginal Effect Visualization

To explore potential non-linearities, we estimate marginal effects using a binning approach:

```{r}
out <- interflex(
  Y = "residual_weight",
  D = "treatment_dummy",
  X = "terracedhouses",
  FE = c("route", "week"),
  data = waste,
  estimator = "binning",
  cutoffs = c(76, 77.5),
  na.rm = TRUE
)

plot(out)
```

